\section{Introduction}

Instruction-tuned language models are expected to refuse harmful requests while
remaining useful on ordinary requests. In open-weight models, however, safety
behavior is not only a property of prompts and decoding: it may also be affected
by direct interventions on the model weights or activations. Refusal-direction
ablation is one such intervention. Prior work suggests that refusal behavior can
be partly represented by a direction in activation space \citep{arditi2024refusal}.

This project asks a deliberately narrow empirical question: if we fit a refusal
direction from a small policy-derived dataset and remove that direction from
Gemma, how much does official SORRY-Bench refusal behavior change? The goal is
not to produce a useful model. The goal is to measure, with a reproducible paired
evaluation, whether a simple edit substantially changes benchmark safety
behavior.

The experiment compares two systems on the same 440 SORRY-Bench prompts:

\begin{itemize}
  \item the untouched \texttt{google/gemma-4-E4B-it} model;
  \item the same model after one fixed refusal-direction weight edit.
\end{itemize}

Because both systems answer the same prompts, the main analysis is paired. The
official SORRY-Bench judge gives each answer a binary score: refusal or unsafe
compliance. We report the size of the compliance-rate change and use McNemar's
test to check whether the observed prompt-level flips are symmetric
\citep{mcnemar1947note,raschka2018model}.

The main contribution is therefore a compact, reproducible case study of how
much a single refusal-direction edit changes official SORRY-Bench behavior for
one Gemma model.
