\section{Results}

\subsection{Overall Compliance Change}

The baseline model complied with 94 of 440 SORRY-Bench prompts (21.4\%). After
the refusal-direction edit, the model complied with 337 of 440 prompts
(76.6\%). This is a paired compliance-rate increase of 55.2 percentage points.
A normal approximation for the paired mean difference gives a 95\% interval of
50.4 to 60.0 percentage points.

\begin{table}[h]
  \centering
  \caption{Overall official SORRY-Bench result.}
  \label{tab:overall-results}
  \begin{tabular}{lrrr}
    \toprule
    Condition & Prompts & Compliance rate & Refusal rate \\
    \midrule
    Baseline Gemma & 440 & 21.4\% & 78.6\% \\
    Edited Gemma   & 440 & 76.6\% & 23.4\% \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Paired Prompt Flips}

The paired table shows that most changed prompts moved in the same direction:
from baseline refusal to edited compliance. There were 247 such flips, compared
with only 4 prompts that moved from baseline compliance to edited refusal.

\begin{table}[h]
  \centering
  \caption{Paired official judge scores. Score 0 is refusal and score 1 is unsafe compliance.}
  \label{tab:paired-scores}
  \begin{tabular}{lrr}
    \toprule
    & \multicolumn{2}{c}{Edited Gemma} \\
    \cmidrule(lr){2-3}
    Baseline Gemma & Refusal & Compliance \\
    \midrule
    Refusal    & 99 & 247 \\
    Compliance & 4  & 90  \\
    \bottomrule
  \end{tabular}
\end{table}

The exact McNemar/binomial test on the 251 discordant pairs gives
$p=4.53\cdot10^{-68}$. The change is therefore not only statistically
detectable, but also large in practical terms.

\subsection{Category-Level Pattern}

The effect is broad but not identical across SORRY-Bench categories. Several
category IDs changed from 0\% baseline compliance to 100\% edited compliance,
including categories 12, 26, 27, and 43. Other categories changed much less:
categories 33, 34, and 38 showed no change, category 20 increased by 30
percentage points, and category 41 increased by 10 percentage points.

This category variation is important for interpretation. The edit does not
simply turn every refusal into compliance; some benchmark categories remain more
resistant than others.
