\section{Discussion}

The experiment shows that a single refusal-direction edit can substantially
change official SORRY-Bench behavior for this Gemma model. The edited model is
not a newly trained checkpoint; it is the same model after a deterministic
weight intervention. Nevertheless, the official judge scores change from mostly
refusal to mostly compliance on the benchmark.

The result supports the view that at least part of refusal behavior is
concentrated enough to be affected by a simple direction edit. The local
policy-area check gives additional support for this interpretation: directions
fit from different policy areas point in similar layerwise directions. This does
not prove that all safety behavior is one-dimensional, but it shows that the
construction data contains a stable refusal-related signal.

\subsection{What the Result Does and Does Not Show}

The main result is a benchmark result. It shows that the official SORRY-Bench
judge is much more likely to classify the edited model's answers as compliant.
It does not prove that every answer is maximally harmful, nor does it measure
general helpfulness, factuality, or conversational quality. The binary judge
score is useful because it is reproducible and official, but it is still a
coarse measurement.

The result also should not be read as evidence that Gemma has no deeper safety
mechanisms. Some categories remain comparatively resistant to the edit. The
category-level pattern suggests that refusal behavior is not uniform across all
harm types.

\subsection{Benchmarking Implication}

The experiment illustrates a limitation of static refusal benchmarks for
open-weight models. A model can have a high refusal rate on a fixed benchmark,
yet a cheap post-hoc edit can greatly change that score. This does not make the
benchmark useless: without a benchmark, the change would be hard to measure. It
does mean that refusal rate alone is not the same as robustness to weight or
activation editing.

\subsection{Limitations}

The construction dataset is synthetic and policy-derived. Its purpose is to
create a controlled refusal direction, not to represent natural user traffic.
The final evaluation uses only one model family, one edited checkpoint, one
decoding setup, and one official judge. The analysis also uses SORRY-Bench as
the main external benchmark, so conclusions should be limited to this evaluation
setting.

Finally, harmful prompts and unsafe outputs are part of the measurement process.
The report therefore reports aggregate rates and paraphrases category behavior
rather than reproducing unsafe prompt text or model outputs.
